A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-18 latex/main.tex

% %%%  The resource availability section is required
% %%%  for all research articles. This component
% %%%  has 3 subsections: "lead contact," "materials
% %%%  availability," and "data and code availability."
% %%%  All 3 subsections must be included, even if no
% %%%  unique materials were generated in the study.
% %%%  Do not edit or change the names of the subheadings.
% %%%  No other subheadings or text are allowed in the
% %%%  resource availability section.

% \subsection*{Lead contact}

% %%%  Authors are required to designate a lead contact,
% %%%  who will be responsible for communication with
% %%%  the journal before and after publication and is
% %%%  the arbiter of disputes, including concerns
% %%%  related to reagents or resource sharing. Only
% %%%  one author can be named the lead contact, and
% %%%  only the lead contact’s information may be
% %%%  provided in this section.

% Requests for further information and resources
% should be directed to and will be fulfilled
% by the lead contact, XX (XX@university.edu).

% \subsection*{Materials availability}

% %%%  This subsection must include a statement describing
% %%%  the availability of newly generated materials
% %%%  associated with the paper, including any conditions
% %%%  for access. If there are no newly generated materials
% %%%  associated with the paper, the statement should
% %%%  state this, e.g.: This study did not generate new
% %%%  materials.

% This study did not generate new materials.

@@

SHZ is supported by an NDPH Intermediate Research Fellowship
(Oxford Population Health, University of Oxford). 
% JK: Commenting this out until exact wording is provided. I'm pretty
% sure that "Wellcome trust" is wrong.
% IG is supported by the Wellcome trust (DPhil in Genomic Medicine and Statistics).
DSP acknowledges funding administered by the Danish National Research Foundation in support of the Pioneer Centre for SMARTbiomed. 
% "acknowledges support" here means "was awarded this grant 
% and it supported this research"
SO acknowledges support from the Natural Sciences and Engineering Research Council of Canada (RGPIN-2022-03726).
JK acknowledges support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation. For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.

@@

% \section*{AUTHOR CONTRIBUTIONS}

% %%%  This component is required for most research papers.
% %%%  Mention each individual author with a statement
% %%%  outlining the contribution of each author to the work.

% Conceptualization, S.C.P. and S.Y.W.;
% methodology, A.B., S.C.P., and S.Y.W.;
% investigation, M.E., A.N.V., N.A.V., S.C.P., and S.Y.W.;
% writing-–original draft, S.C.P. and S.Y.W.;
% writing-–review \& editing, S.C.P. and S.Y.W.;
% funding acquisition, S.C.P. and S.Y.W.;
% resources, M.E.V and C.K.B.;
% supervision, A.B., N.L.W., and A.A.D.

% \section*{DECLARATION OF INTERESTS}

% %%%  This component is required for all articles, even
% %%%  if the authors have no competing interests; if
% %%%  this is the case, insert "The authors declare no
% %%%  competing interests." Please refer to the
% %%%  declaration of interests policy:
% %%%  https://www.cell.com/declaration-of-interests

% % TODO: Close https://github.com/jeromekelleher/sc2ts-paper/issues/922
% The authors declare no competing interests.

% \section*{DECLARATION OF GENERATIVE AI AND AI-ASSISTED TECHNOLOGIES}

% %%%  If generative AI and AI-assisted technologies
% %%%  were used in the writing process, this must
% %%%  be disclosed in the paper. This declaration
% %%%  does not apply to the use of basic tools for
% %%%  checking grammar, spelling, references, etc.
% %%%  If you have nothing to disclose, please do not
% %%%  include this component.

% During the preparation of this work, the author(s) used ChatGPT
% in order to obtain editorial input on the text.
% After using this tool or service, the author(s) reviewed
% and edited the content as needed and take(s) full responsibility for the content of the publication.

>>>>

%%%  The resource availability section is required
%%%  for all research articles. This component
%%%  has 3 subsections: "lead contact," "materials
%%%  availability," and "data and code availability."
%%%  All 3 subsections must be included, even if no
%%%  unique materials were generated in the study.
%%%  Do not edit or change the names of the subheadings.
%%%  No other subheadings or text are allowed in the
%%%  resource availability section.

\subsection*{Lead contact}

%%%  Authors are required to designate a lead contact,
%%%  who will be responsible for communication with
%%%  the journal before and after publication and is
%%%  the arbiter of disputes, including concerns
%%%  related to reagents or resource sharing. Only
%%%  one author can be named the lead contact, and
%%%  only the lead contact’s information may be
%%%  provided in this section.

Requests for further information and resources
should be directed to and will be fulfilled
by the lead contact, Shing H. Zhan (shing.zhan@ndph.ox.ac.uk).

\subsection*{Materials availability}

%%%  This subsection must include a statement describing
%%%  the availability of newly generated materials
%%%  associated with the paper, including any conditions
%%%  for access. If there are no newly generated materials
%%%  associated with the paper, the statement should
%%%  state this, e.g.: This study did not generate new
%%%  materials.

This study did not generate new materials.

@@

SHZ acknowledges support from
Oxford Population Health, University of Oxford
(NDPH Intermediate Research Fellowship)
and
% Apparently, it is now Johnson & Johnson Innovative Medicine.
Janssen Pharmaceuticals
(Oxford-Janssen Translational Genomics Fellowship).
% JK: Commenting this out until exact wording is provided. I'm pretty
% sure that "Wellcome trust" is wrong.
% IG is supported by the Wellcome trust (DPhil in Genomic Medicine and Statistics).
DSP acknowledges funding administered by the Danish National Research Foundation in support of the Pioneer Centre for SMARTbiomed. 
% "acknowledges support" here means "was awarded this grant 
% and it supported this research"
SO acknowledges support from the Natural Sciences and Engineering Research Council of Canada (RGPIN-2022-03726).
JK acknowledges support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation. For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.

@@

\section*{AUTHOR CONTRIBUTIONS}

%%%  This component is required for most research papers.
%%%  Mention each individual author with a statement
%%%  outlining the contribution of each author to the work.

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, everyone;
funding acquisition, JK;
resources, JK;
supervision, JK.

\section*{DECLARATION OF INTERESTS}

%%%  This component is required for all articles, even
%%%  if the authors have no competing interests; if
%%%  this is the case, insert "The authors declare no
%%%  competing interests." Please refer to the
%%%  declaration of interests policy:
%%%  https://www.cell.com/declaration-of-interests

% TODO: https://github.com/jeromekelleher/sc2ts-paper/issues/922
The authors declare no competing interests.

\section*{DECLARATION OF GENERATIVE AI AND AI-ASSISTED TECHNOLOGIES}

%%%  If generative AI and AI-assisted technologies
%%%  were used in the writing process, this must
%%%  be disclosed in the paper. This declaration
%%%  does not apply to the use of basic tools for
%%%  checking grammar, spelling, references, etc.
%%%  If you have nothing to disclose, please do not
%%%  include this component.

% https://github.com/jeromekelleher/sc2ts-paper/issues/923
During the preparation of this work, the author(s) used ChatGPT
in order to obtain editorial input on the text.
After using this tool or service, the author(s) reviewed
and edited the content as needed and
take(s) full responsibility for the content of the publication.
